\section{Documentation Requirements}

\subsection{License}

\subsubsection{Registration License}

In order to provide better service to our users, users shall claim to
agree our registration license when applying for an account. The
registration license shall cover the following parts:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Rules on using our service, including the constrains on using,
  transfering the account, the limited use of the information we
  provided.
\item
  The privacy on the personal information provided by users in
  registration.
\item
  User shall understand and accept the service provided by Uknow before
  registration, and take full responsibilities for any kind of abuse of
  our service.
\end{enumerate}

\subsubsection{Disclaimers}

In order to avoid unnecessary conflicts with our users, users must sign
our disclaimers before using the information collector of Uknow InfoHub.
The disclaimer shall cover the following contents:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Uknow is not responsible for, and expressly disclaims all liability
  for, damages of any kind arising out of use, reference to, or reliance
  on any information provided by Uknow.
\item
  While the information provided by Ukonw is periodically updated, no
  guarantee is given that the information is correct, complete, and
  up-to-date.
\item
  Though Uknow might provide links or direct data from other Internet
  Resources, Uknow is not responsible for any kind of damages arising
  out of visit to those sites.
\item
  Uknow doesn't own and shall not preserve copyright for any information
  provided in our service, but will show the user the origin of those
  information. Any kind of offence to the copyright of the original
  author of the information provided by us is seen as a direct offence
  to the author.
\item
  Though Uknow might contain advertisements or other types of
  endorsement for products or services from third-party companies, Uknow
  has not investigated and does not assure the fidelity of the claims by
  any advertiser. Product information is based solely on material
  received from suppliers.
\end{enumerate}

\subsubsection{Notice to Right Holders}

Uknow InfoHub developer group understand and respect the right of any
individual or entity. Thus, a notice to right holders must be provided
on our website for right holders to read and get instructions on
enforcement of their corresponding rights related to the behavior or the
services provided by Uknow InfoHub developer group. The notice shall
cover the following parts:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Copyright. While Uknow InfoHub provides simple information aggregation
  for our terminal users, Uknow respects and does not offend the
  copyright of the original author of the information presented by us.
\item
  Privacy. Uknow might fetch and parse information from various sources,
  but with the authority of our service users. Uknow will not
  initiatively collect private data of any individual or entity.
\item
  Use of our service. All users of our services are immediately granted
  the right of using our service according to the user agreement right
  after registration.
\end{enumerate}

\subsection{Help Manual}

\subsubsection{Basic Use of Our Service}

For the purpose of getting users quickly involved in our product, an
instruction manual on the basic use of our service is necessary. This
instruction manual shall contain the following parts:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The functionality of our service, and the instructions of using them
  on our clients.
\item
  Examples on the use of our key functionality, including tab-like
  information classification, auto-tagging, etc.
\item
  Precautions and attentions that our users should be aware of.
\end{enumerate}

\subsubsection{API Documentation}

Since Uknow InfoHub provides an extensible and flexible structure,
allowing developers to create their own plugins to extend the
functionalities of Uknow, an open API documentation is needed for
potential developers to read and develop their plugins for our platform
accordingly. Meanwhile, as the scale of this project grows, there will
be inevitable difficulty in its maintainance and update. Therefore, an
detailed API documentation of internal classes and interfaces is also
necessary for the everlasting development of this project.

The API documentation of Uknow should be presented in good-looking
style, in cross-platform formats(HTML, pdf, etc.), and be easy to refer
to. The names of classes and terms in the documentation should be well
referenced to its definition, providing readers with better readability.
