\section{Interface}
  \subsection{Inner Interface}
    Interfaces that shouldn't be called or even seen by client are considered as inner interfaces.
    Mainly they are providing functions among components.

    This section shall describe the usage of each interface,
    but we maintained a well constructed API document which describes each part of this project with explicit details.
    So, another duplicate description is not that useful,
    will causing more resources to maintain and may cause disagreements after changing some part of interfaces.

    In a word, referring to API document is suggested when want to look up for one interface.

  \subsection{Client Interface}
    This part will discuss with caution dreadfully,
    for that interfaces may changed a lot when developing.
    Part that we can be sure of is that JSON is used when communicating between client and API server.
    Then the API server will call various methods provided by different classes that fit the requests.

    For that this project is still in the bootstrapping step, and it may change everyday, we decided to maintain the interface information with
    wiki and API document, other than write it done on paper.
    Meanwhile, requests' format is still under discussion and it would change a lot. We don't think providing them now is a good idea.

    More, the prototype system does not containing a client program and user involved part,
    so there's no need for stable client interfaces' design up to now.

