\section{Test Evaluation}
\label{sec:test_evaluation}
  \subsection{Software}
    \subsubsection{Functional}
      All APIs do the right work as what they are designed for.
      And all APIs is robust even under sedulous injection or other kind of inroads.
      Getting this result shows that the develop team knows lots of knowledge in network security field, and does a good design at the very beginning.
    \subsubsection{Performance}
      Both average performance and common performance are quite well, but there are still some work to do to speed worst case up.
      However, the enhancement is limited, for in worst case the API will return plenty of data, and the bottleneck is network transform.

      So, may a increment request API is needed in the future.
      This kind of API will remember what they has provided and won't give them out again and again but it has changed.

      Even though, the worst response time is admissible by user, so further enhancement can be arrested until it really make sense.
  \subsection{Test}
    \subsubsection{Functional}
      Functional test includes legal and illegal cases, considered boundary situation and uncommon use case.
      Besides, many common injection case are used, to test the security of the APIs.
      This part of test cases are really completed and cover many professional assault method.
    \subsubsection{Performance}
      For better result that determines where the bottle neck is maybe a enhancement for the performance test.
      Current result only shows the response time for whole APIs but doesn't have details like network transform time and database query time.
      So further enhancement may don't have critical target or was done on unimportant part.

