\section{Test Procedure}
\label{sec:test_procedure}
  \subsection{Testers}
    zxytim, ppwwyyxx, vuryleo, jiakai
  \subsection{Period}
    18:00 Dec 13th, 2013 to 18:00 Dec 14th, 2013.
  \subsection{Functional Tests}
    \subsubsection{Test Case Designing}
      First, read the API list, select out APIs that need to be tested.
      Then, design use cases for each API base on its function.
      At last, transform test cases into proper request format and add them into the test suite.

      After all, several cases that designed to test the robustness of the APIs are recorded as well.
      These cases will perform illegal request such as wrong format, permission overstep and injection.
    \subsubsection{Environment Setting}
      At first, use virtualenv to build a virtual python environment for this project.
      Then use install tool located in manage suite to set up runtime environment for it.

      In order to provide production environment, a mongodb server and a redis server is also required.
    \subsubsection{Software Configuring}
      In this test, the default configure is applied. So no action is needed in this step.
    \subsubsection{Test Configuring}
      In order to test some third party function, correct authentication information is required.
      The configure file can be found easily in test suite.
    \subsubsection{Test Executing}
      Execute test entry scripts to do the tests.
    \subsubsection{Log Analyzing}
      After getting the test log, parse the useful information out and ordinate them into proper format.
  \subsection{Performance Tests}
    \subsubsection{Test Case Designing}
      Several APIs that may have heavy loads are picked out to get the worst performance data.
      Then a random set of APIs is generated in order to test the average performance.
      Besides, some APIs that may be requested most frequently are selected to get the common performance.

      After all, translate the test requests in functional test into well formed Internet requests
      and put them in proper places.
    \subsubsection{Environment Setting}
      In propose of simulating real world performance,
	  client and server are located on different machines, so the network
	  transmission is considered.

	  To do so, deploy the project in production mode on one machine, and get
	  the test suite on another.

	  Network throughput benchmark is tested using ApacheBench\footnote{http://httpd.apache.org/docs/2.2/programs/ab.html}, with concurrency of 4 and 10,000 requests on each API.
	  The CPU, memory and IO count usage of server program will be intensively examined.

    \subsubsection{Test Executing}
      Execute test entry scripts to do the tests.
    \subsubsection{Log Analyzing}
      Performance test will generate plenty of log.
      So a data visualization procedure is taken to display the data in different collections and patterns.
